Datasheet for NHANES dataset

### 2024-12-14 other/datasheet/datasheet_template.qmd
updatated datasheet

---
title: "Datasheet for NHANES dataset'"
author: 
  - Sakura Hu
thanks: "Code and data are available at: https://github.com/xycww/BMI/tree/main."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: datasheetreference.bib
---

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The National Health and Nutrition Examination Survey (NHANES) was created to assess the health and nutritional status of adults and children in the United States. The survey combines both interviews and physical examinations to gather comprehensive health data. The primary task of NHANES is to provide vital statistics on the nation’s health, enabling public health experts, policymakers, and researchers to track trends in nutrition, health behaviors, and the prevalence of chronic diseases. The resampled version of NHANES data, which is utilized in this analysis, has been adapted specifically for educational purposes. This version of the data corrects for the oversampling of certain populations (e.g., racial minorities) to ensure a more accurate representation of the U.S. population. The aim of this adjustment is to make the dataset suitable for educational use, enabling students and researchers to analyze and learn from it while avoiding potential biases introduced by the original survey's complex sampling methods. This resampling version helps simplify the dataset and facilitates learning without compromising the integrity of the data collection process.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The NHANES dataset was created by the National Center for Health Statistics (NCHS), which is part of the Centers for Disease Control and Prevention (CDC). NCHS is responsible for producing and maintaining vital health statistics in the United States. The resampled data was assembled by Michelle Dalrymple of Cashmere High School and Chris Wild of the University of Auckland, New Zealand for educational purposes.

@@

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instances in the National Health and Nutrition Examination Survey (NHANES) dataset represent individuals (people) from the non-institutionalized civilian population of the United States.

@@

	The sample is designed to be representative of the larger U.S. population, but with oversampling of certain subpopulations such as racial minorities, low-income individuals, and the elderly. These oversampling strategies are employed to ensure that there is sufficient data to generate reliable estimates for these groups, which may be underrepresented in a simple random sample. For example, the NHANES oversamples non-Hispanic Black, Hispanic, low-income White persons, and individuals aged 80 and older.

	To make the sample representative of the entire U.S. population, weights are applied to account for the oversampling and to adjust for differential probabilities of selection. This allows the data to be treated as if it were a simple random sample, and the weighted results can be generalized to the broader population. The representativeness of the sample is verified through the use of these weights and by ensuring that the sample covers various geographic regions of the U.S., including both metropolitan and non-metropolitan areas. Additionally, the NHANES sampling design has been rigorously tested and adjusted to ensure that it accurately reflects the population in terms of demographic factors.

@@

6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- The NHANES dataset contains missing data, which can be categorized as either unit nonresponse or component/item nonresponse. Unit nonresponse occurs when an individual selected to participate in the survey does not respond during either the interview or examination phase. For example, during the 2009-2010 cycle, of the 13,272 individuals eligible for participation, only 10,537 completed the household interview, leading to an interview nonresponse rate of 21%. Furthermore, of the interviewed participants, only 10,253 participated in the Medical Examination Center (MEC) examination, contributing to an additional 2% of nonresponse during the examination phase. This nonresponse is addressed by applying sample weights that adjust for the nonresponse. Component/item nonresponse refers to missing data from specific survey components, such as not all participants opting to complete a particular health examination (e.g., a blood pressure measurement). Additionally, NHANES uses specific codes for missing values, such as a period (.) for numeric variables and blank spaces for character variables. Responses like "refused" or "don't know" are also treated as missing and are assigned specific codes (e.g., 7, 77, or 777 for "refused" and 9, 99, or 999 for "don't know"). These should also be treate as missing data to avoid distorting analysis results.

@@

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- there are no formal recommendations for typical splits such as training, development/validation, and testing. However, given the structure and design of NHANES, there are important considerations for subsetting and combining data that influence how data is prepared for analysis. Since NHANES uses a complex, multi-stage sampling design, any analysis must account for the sampling weights and stratification to avoid bias.

@@

13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- Yes, the NHANES dataset identifies several subpopulations based on demographic and socioeconomic characteristics.
	- Age is recorded in years and categorized into decades. The dataset includes participants across a wide age range, with individuals aged 80 and over intentionally oversampled to ensure adequate representation of this subgroup.
	- Race is categorized as Mexican, Hispanic, White, Black, Asian, or Other. Non-Hispanic Black persons and Hispanic persons are intentionally oversampled to improve the reliability and precision of estimates for these subpopulations.
	- Income is categorized using a poverty ratio, which reflects a range of socioeconomic statuses, with specific attention given to low-income white groups.
	- Gender is categorized as male and female, with the dataset typically having an approximately equal distribution of males and females.

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, it is not possible to identify individuals from the dataset

@@

	Furthermore, the dataset includes biometric data such as weight, height, and blood test results. While NHANES does not include genetic data or government identification numbers (such as Social Security numbers), the presence of health and demographic variables may still pose confidentiality risks if improperly handled. However, strict measures are in place to protect participant privacy, including anonymization, ethical review processes, and federal confidentiality protections.

@@

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data associated with each instance in the NHANES dataset was primarily acquired through both directly observable measurements and self-reported survey responses. For instance, health data such as blood pressure, body mass index (BMI), and laboratory test results were directly measured during health examinations conducted at mobile examination centers (MECs). These direct observations are objective and typically subject to standardized procedures to ensure accuracy and consistency.

	In contrast, demographic and lifestyle information (e.g., age, gender, race, smoking habits, physical activity) were self-reported by participants through structured interviews. This data is subjective and relies on the accuracy and honesty of the respondents.

	To enhance the reliability of the dataset and minimize biases, the self-reported data was verified and validated in several ways. First, sample weights are applied to correct for unequal probabilities of selection and nonresponse. For example, oversampling of certain subpopulations, like racial minorities and low-income groups, was performed, and the sample weights adjust for these oversampling techniques.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Health Examinations and Laboratory Tests: Data such as blood pressure, height, weight, BMI, and other health measurements were collected during in-person visits to mobile examination centers (MECs). These centers are equipped with specialized medical equipment to directly measure participants’ health metrics. The collection of these data points is validated by well-established clinical protocols and the use of calibrated equipment to ensure the accuracy of the measurements.
	- Survey Interviews: Participants also answered detailed surveys that included demographic, socioeconomic, and lifestyle-related questions. This data was gathered through structured interviews conducted by trained personnel using electronic devices such as tablets. The interviewers followed strict protocols to ensure uniformity across interviews and minimize errors. For instance, if a participant was unable to understand or respond in English, interpreters were made available to facilitate communication. The responses provided by participants were validated by cross-referencing answers within the survey and ensuring consistency across different sections. The interviewers followed strict protocols to ensure uniformity across interviews and minimize errors. The responses provided by participants were validated by cross-referencing answers within the survey and ensuring consistency across different sections.

@@

	- Sample selection for NHANES followed 4 stages:
	Primary Sampling Units (PSUs): In the first stage, primary sampling units, which are typically counties or groups of contiguous counties, are selected with probability proportional to size (PPS). This means that PSUs with larger populations have a higher probability of being selected. This approach helps ensure that the sample reflects the distribution of the population, with oversampling occurring for certain groups of interest, such as racial minorities, to improve the reliability of estimates for these subgroups.

Segmentation: After selecting the PSUs, the next stage involves dividing the selected PSUs into smaller segments, typically geographic units such as city blocks. These segments are then chosen using PPS to ensure an adequate representation of different population groups.

Dwelling Units (DUs): The third stage involves selecting dwelling units (households) within the chosen segments. In areas with higher concentrations of specific groups, such as low-income or minority populations, these households are selected at a higher rate to ensure proper representation of these groups.

Selection of Individuals: In the final stage, individuals are randomly selected from within the households. The selection is done within designated age, sex, and race/ethnicity subdomains to achieve a balance across these demographic characteristics. This step ensures that the sample includes a diverse range of individuals and that subgroups, such as the elderly or certain racial/ethnic populations, are adequately represented.

- To ensure that specific demographic subgroups are sufficiently represented, NHANES uses oversampling techniques. For example, non-Hispanic black, Hispanic, and low-income white individuals, as well as those aged 80 and older, are oversampled. This oversampling allows for more precise estimates for these groups, which may otherwise be underrepresented in a simple random sample.

- Due to the complex sampling design, sample weights are applied to adjust for unequal probabilities of selection and to account for nonresponse. These weights allow analysts to produce nationally representative estimates, as they correct for the oversampling of certain subgroups and for any nonresponse bias.

@@

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Yes, ethical review processes were conducted for the NHANES dataset. The NHANES protocol was developed and reviewed to be in compliance with the U.S. Department of Health and Human Services (HHS) Policy for Protection of Human Research Subjects, as outlined in 45 CFR part 46, which can be accessed at [HHS Policy for Protection of Human Research Subjects](http://www.hhs.gov/ohrp/humansubjects/guidance/45cfr46.html).

@@

8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*

	![consent form](/Users/hxw/marriage/other/datasheet/consent.png)

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- yes, and it is shown in the consent form provided.

10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- yes, and this information is shown at [participant FAQ](https://www.cdc.gov/nchs/nhanes/participant/participant-faq.htm).

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- NHANES uses specific codes for "refused" and "don't know" responses, assigning values such as 7, 77, or 777 for refusals, and 9, 99, or 999 for "don't know" responses.

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Yes, the NHANES dataset has been used extensively in a variety of tasks related to public health research and analysis. Since its inception, the dataset has been used to assess the health and nutritional status of the U.S. population, providing valuable insights into a wide range of health indicators, including obesity, diabetes, cardiovascular diseases, and other chronic conditions. Researchers have used NHANES data to analyze the prevalence of different health conditions, identify risk factors, evaluate the impact of lifestyle choices (such as diet, physical activity, and smoking) on health outcomes, and inform public health policies.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- Some of the product can be found [here](https://www.cdc.gov/nchs/nhanes/nhanes_products.htm).

@@

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The data can be downloaded directly from the NHANES page on the CDC official website

3. *When will the dataset be distributed?*
	- The NHANES 2009-2010 data were made available after the data collection period ended

4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- Data Use Agreement can be found at [this website](https://www.cdc.gov/nchs/policy/data-user-agreement.html)

5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- DLicensing terms and fees associated with restriction can be found at [the website](https://www.cdc.gov/nchs/policy/data-user-agreement.html)

6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No

@@

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- You can contact NHANES staff by calling 1 (800) 232-4636

>>>>

---
title: "Datasheet for NHANES dataset'"
author: 
  - Sakura Hu
thanks: "Code and data are available at: https://github.com/xycww/BMI."
date: today
date-format: long
format: pdf
resource-paths: ["other/datasheet"]
number-sections: true
bibliography: datasheetreference.bib
---

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The National Health and Nutrition Examination Survey (NHANES) was created to assess the health and nutritional status of adults and children in the United States. The survey combines both interviews and physical examinations to gather comprehensive health data [@nhanes]. The primary task of NHANES is to provide vital statistics on the nation’s health, enabling public health experts, policymakers, and researchers to track trends in nutrition, health behaviors, and the prevalence of chronic diseases. The resampled version of NHANES data, which is utilized in this analysis, has been adapted specifically for educational purposes [@nhanes]. This version of the data corrects for the oversampling of certain populations to ensure a more accurate representation of the U.S. population. The aim of this adjustment is to make the dataset suitable for educational use, enabling students and researchers to analyze and learn from it while avoiding potential biases introduced by the original survey's complex sampling methods [@nhanes]. This resampling version helps simplify the dataset and facilitates learning without compromising the integrity of the data collection process.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The NHANES dataset was created by the National Center for Health Statistics (NCHS), which is part of the Centers for Disease Control and Prevention (CDC). NCHS is responsible for producing and maintaining vital health statistics in the United States. The resampled data was assembled by Michelle Dalrymple of Cashmere High School and Chris Wild of the University of Auckland, New Zealand for educational purposes [@nhanes].

@@

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instances in the National Health and Nutrition Examination Survey (NHANES) dataset represent individuals (people) from the non-institutionalized civilian population of the United States [@nhanes].

@@

	The sample is designed to be representative of the larger U.S. population, but with oversampling of certain subpopulations such as racial minorities, low-income individuals, and the elderly. These oversampling strategies are employed to ensure that there is sufficient data to generate reliable estimates for these groups, which may be underrepresented in a simple random sample. For example, the NHANES oversamples non-Hispanic Black, Hispanic, low-income White persons, and individuals aged 80 and older [@sample].

	To make the sample representative of the entire U.S. population, weights are applied to account for the oversampling and to adjust for differential probabilities of selection. This allows the data to be treated as if it were a simple random sample, and the weighted results can be generalized to the broader population. The representativeness of the sample is verified through the use of these weights and by ensuring that the sample covers various geographic regions of the U.S., including both metropolitan and non-metropolitan areas [@sample]. Additionally, the NHANES sampling design has been rigorously tested and adjusted to ensure that it accurately reflects the population in terms of demographic factors [@sample].

@@

6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- The NHANES dataset contains missing data, which can be categorized as either unit nonresponse or component/item nonresponse. Unit nonresponse occurs when an individual selected to participate in the survey does not respond during either the interview or examination phase [@analytic]. For example, during the 2009-2010 cycle, of the 13,272 individuals eligible for participation, only 10,537 completed the household interview, leading to an interview nonresponse rate of 21% [@analytic]. Furthermore, of the interviewed participants, only 10,253 participated in the Medical Examination Center (MEC) examination, contributing to an additional 2% of nonresponse during the examination phase [@analytic]. This nonresponse is addressed by applying sample weights that adjust for the nonresponse [@analytic]. Component/item nonresponse refers to missing data from specific survey components, such as not all participants opting to complete a particular health examination (e.g., a blood pressure measurement). Additionally, NHANES uses specific codes for missing values, such as a period (.) for numeric variables and blank spaces for character variables [@analytic]. Responses like "refused" or "don't know" are also treated as missing and are assigned specific codes (e.g., 7, 77, or 777 for "refused" and 9, 99, or 999 for "don't know") [@analytic]. These should also be treated as missing data to avoid distorting analysis results.

@@

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- there are no formal recommendations for typical splits such as training, development/validation, and testing. However, given the structure and design of NHANES, there are important considerations for subsetting and combining data that influence how data is prepared for analysis. Since NHANES uses a complex, multi-stage sampling design, any analysis must account for the sampling weights and stratification to avoid bias [@analytic].

@@

13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- Yes, the NHANES dataset identifies several subpopulations based on demographic and socioeconomic characteristics.
	- Age is recorded in years and categorized into decades. The dataset includes participants across a wide age range, with individuals aged 80 and over intentionally oversampled to ensure adequate representation of this subgroup [@sample].
	- Race is categorized as Mexican, Hispanic, White, Black, Asian, or Other. Non-Hispanic Black persons and Hispanic persons are intentionally oversampled to improve the reliability and precision of estimates for these subpopulations [@sample].
	- Income is categorized using a poverty ratio, which reflects a range of socioeconomic statuses, with specific attention given to low-income white groups [@sample].
	- Gender is categorized as male and female, with the dataset typically having an approximately equal distribution of males and females [@sample].

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, it is not possible to identify individuals from the dataset. Data were edited such that all direct personal identifiers, as well as any characteristics that could lead to identification, were omitted from the data sets [@plan].

@@

	Furthermore, the dataset includes biometric data such as weight, height, and blood test results. While NHANES does not include genetic data or government identification numbers, the presence of health and demographic variables may still pose confidentiality risks if improperly handled. However, strict measures are in place to protect participant privacy, including anonymization, ethical review processes, and federal confidentiality protections [@plan].

@@

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data associated with each instance in the NHANES dataset was primarily acquired through both directly observable measurements and self-reported survey responses. For instance, health data such as blood pressure, body mass index (BMI), and laboratory test results were directly measured during health examinations conducted at mobile examination centers (MECs) [@plan]. These direct observations are objective and typically subject to standardized procedures to ensure accuracy and consistency.

	In contrast, demographic and lifestyle information (e.g., age, gender, race, smoking habits, physical activity) were self-reported by participants through structured interviews [@plan]. This data is subjective and relies on the accuracy and honesty of the respondents.

	To enhance the reliability of the dataset and minimize biases, self-reported data were verified and validated through multiple approaches. First, cross-validation with objective measures was performed whenever possible [@plan]. Standardized questionnaires, designed based on validated instruments and periodically reviewed, were administered by trained interviewers to ensure consistency in data collection [@plan]. Built-in logic checks identified implausible or inconsistent responses during interviews, prompting clarifications or follow-up questions [@plan]. Proxy reporting was allowed when participants, such as children, were unable to respond directly.

Sample weights were applied to correct for unequal probabilities of selection and nonresponse [@plan]. For example, oversampling of subpopulations, including racial minorities and low-income groups, was performed, and sample weights adjusted for these techniques. This comprehensive approach to verification and adjustment reduces bias and enhances the validity of the dataset.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Health Examinations and Laboratory Tests: Data such as blood pressure, height, weight, BMI, and other health measurements were collected during in-person visits to mobile examination centers (MECs). These centers are equipped with specialized medical equipment to directly measure participants’ health metrics. The collection of these data points is validated by well-established clinical protocols and the use of calibrated equipment to ensure the accuracy of the measurements [@plan].
	- Survey Interviews: Participants also answered detailed surveys that included demographic, socioeconomic, and lifestyle-related questions. This data was gathered through structured interviews conducted by trained personnel using electronic devices such as tablets [@plan]. The interviewers followed strict protocols to ensure uniformity across interviews and minimize errors [@plan]. The responses provided by participants were validated by cross-referencing answers within the survey and ensuring consistency across different sections [@plan].

@@

	- Sample selection for NHANES followed 4 stages:
	- Primary Sampling Units (PSUs): In the first stage, primary sampling units, which are typically counties or groups of contiguous counties, are selected with probability proportional to size (PPS) [@plan]. This means that PSUs with larger populations have a higher probability of being selected [@plan]. This approach helps ensure that the sample reflects the distribution of the population, with oversampling occurring for certain groups of interest, such as racial minorities, to improve the reliability of estimates for these subgroups [@plan].

  - Segmentation: After selecting the PSUs, the next stage involves dividing the selected PSUs into smaller segments, typically geographic units such as city blocks [@plan]. These segments are then chosen using PPS to ensure an adequate representation of different population groups [@plan].

  - Dwelling Units (DUs): The third stage involves selecting dwelling units (households) within the chosen segments [@plan]. In areas with higher concentrations of specific groups, such as low-income or minority populations, these households are selected at a higher rate to ensure proper representation of these groups [@plan].

  - Selection of Individuals: In the final stage, individuals are randomly selected from within the households [@plan]. The selection is done within designated age, sex, and race/ethnicity subdomains to achieve a balance across these demographic characteristics [@plan]. This step ensures that the sample includes a diverse range of individuals and that subgroups, such as the elderly or certain racial/ethnic populations, are adequately represented [@plan].

  - To ensure that specific demographic subgroups are sufficiently represented, NHANES uses oversampling techniques. For example, non-Hispanic black, Hispanic, and low-income white individuals, as well as those aged 80 and older, are oversampled [@plan]. This oversampling allows for more precise estimates for these groups, which may otherwise be underrepresented in a simple random sample.

  - Due to the complex sampling design, sample weights are applied to adjust for unequal probabilities of selection and to account for nonresponse [@plan]. These weights allow analysts to produce nationally representative estimates, as they correct for the oversampling of certain subgroups and for any nonresponse bias.

@@

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Yes, ethical review processes were conducted for the NHANES dataset. The NHANES protocol was developed and reviewed to be in compliance with the U.S. Department of Health and Human Services (HHS) Policy for Protection of Human Research Subjects, as outlined in 45 CFR part 46, which can be accessed at [the official website of the U.S. Department of health and human services](http://www.hhs.gov/ohrp/humansubjects/guidance/45cfr46.html).

@@

8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
  - Before being approached by NHANES staff, participants receive an advance letter. This letter outlines the purpose of the survey, the types of data to be collected, and reassures individuals about the confidentiality of their information.
Example text in the letter includes details about why the participant was chosen and how their data will contribute to public health research.

	![advance](advanceletter.png)

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Before any data collection begins, participants are required to sign a written informed consent form. These forms clearly state that participation is voluntary, it provide assurances about privacy and confidentiality, highlighting that data will be used only for research purposes, and offer participants the opportunity to ask questions and withdraw at any point without any repercussions.
		![consent form](consent.png)

10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- yes, NHANES emphasizes that participation is entirely voluntary. Participants are explicitly told that they can refuse to participate in any part of the survey or withdraw from the study entirely at any point during the data collection process without facing any negative consequences. This information is shown at [participant FAQ](https://www.cdc.gov/nchs/nhanes/participant/participant-faq.htm).

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- NHANES uses specific codes for "refused" and "don't know" responses, assigning values such as 7, 77, or 777 for refusals, and 9, 99, or 999 for "don't know" responses [@analytic].

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Yes, the NHANES dataset has been used extensively in a variety of tasks related to public health research and analysis. Since its inception, the dataset has been used to assess the health and nutritional status of the U.S. population, providing valuable insights into a wide range of health indicators, including obesity, diabetes, cardiovascular diseases, and other chronic conditions. Researchers have used NHANES data to analyze the prevalence of different health conditions, identify risk factors, evaluate the impact of lifestyle choices (such as diet, physical activity, and smoking) on health outcomes, and inform public health policies.

2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- Some of the products can be found [here](https://www.cdc.gov/nchs/nhanes/nhanes_products.htm).

@@

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The data can be downloaded directly from the NHANES page on the CDC official website.

3. *When will the dataset be distributed?*
	- The NHANES 2009-2010 data were made available after the data collection period ended.

4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
  - The NHANES dataset is provided under strict confidentiality protections, and data use is limited to statistical analysis. There are severe legal penalties for violating the confidentiality and data use conditions. Users must agree to these terms before using the dataset, ensuring compliance with the applicable laws and ethical guidelines.
	- Data Use Agreement can be found at [this website](https://www.cdc.gov/nchs/policy/data-user-agreement.html)

5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No

6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- There are no export controls or regulatory restrictions like those typically imposed on military or sensitive commercial data. The NHANES dataset is governed by federal confidentiality laws, and users are required to adhere to data use restrictions as outlined in the Data Use Agreement.

@@

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- You can contact NHANES staff by calling 1 (800) 232-4636.
